---
Title: exponential distribution simulation
output:
  pdf_document: default
  html_document:
    keep_md: yes
Author: Qiang Wu
---

 Overview: 
 In this simulation I am trying to simulate the exponential distribution.
 rexp(n,lambda).
The mean of rexp is 1/lambda
The sd of rexp is 1/lambda

In this simulation, lambda = 2.

Sample Mean versus Theoretical Mean: 

```{r, echo=TRUE, cache=TRUE}
suppressPackageStartupMessages(library(ggplot2))
lambda<-2
mns<-NULL
for (i in 1 : 1000) mns<-c(mns, mean(rexp(40,0.2)))
hist(mns)
abline(v=mean(mns),col='red')
```

So our simulated mean is mean(mns) = `r mean(mns)`
And the theoretical mean is `r 1/lambda`

Sample Variance versus Theoretical Variance: Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances.

```{r, echo=TRUE, cache=TRUE}
sds<-NULL
for (i in 1 : 1000) sds<-c(sds, sd(rexp(40,0.2)))
hist(sds)
abline(v=mean(sds),col='red')
```

So our simulated variance is mean(sds) = `r mean(sds)`
And the theoretical sd is `r 1/lambda`

Distribution: To check if mns is approximate normal distribution, we plot mns of rnorm(n=1000, mean=5, sd=5) in the same graph.
```{r, echo=TRUE, cache=TRUE}
d1<-data.frame(x=mns,name="simulation")
d2<-data.frame(x=rnorm(1000,mean=5,sd=5),name="theoretical")
d<-rbind(d1,d2)
ggplot(d,aes(x=x, fill=name))+geom_histogram()
```

From the plot, we can see the means of exp distribution is approximate normal distribution.



