---
Title: Analysis ToothGrowth data
output:
  pdf_document: default
  html_document:
    keep_md: yes
Author: Qiang Wu
---

# Load the ToothGrowth data and perform some basic exploratory data analyses 
```{r, echo=TRUE, cache=TRUE}
data("ToothGrowth")
```

# Provide a basic summary of the data.

```{r,echo=TRUE,cache=TRUE}
summary(ToothGrowth)
```

# Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.
```{r, echo=TRUE, cache=TRUE}
library(ggplot2)
ggplot(ToothGrowth, aes(x=len, fill=supp)) + facet_wrap(~dose) + xlab('tooth length') + ggtitle('distribution of guinea pig tooth lengths') + geom_histogram()
```

## 1. test the len with the dos
```{r, echo=TRUE, cache=TRUE}
t.test(ToothGrowth$len, ToothGrowth$dose, paired=FALSE, var.equal=FALSE)
```
The 95% percent confidence interval doesn't contain 0, that means we can reject the null hypothesis. Means tooth len is related to the dose.

## 2. test the len with the supp in low does
```{r, echo=TRUE, cache=TRUE}
d1<-ToothGrowth[ToothGrowth$dose==0.5,]
t.test(d1[d1$supp=="VC",]$len, d1[d1$supp=="OJ",]$len, paired=FALSE, var.equal=FALSE)
```
The 95% percent confidence interval doesn't contain 0, that means we can reject the null hypothesis. Means in low dose, tooth len is related to suppliment.

## 3. test the len with the supp in median dose
```{r, echo=TRUE, cache=TRUE}
d2<-ToothGrowth[ToothGrowth$dose==1.0,]
t.test(d2[d2$supp=="VC",]$len, d2[d2$supp=="OJ",]$len, paired=FALSE, var.equal=FALSE)
```
The 95% percent confidence interval doesn't contain 0, that means we can reject the null hypothesis. Means in median dose, tooth len is related to the suppliment.

## 4. test the len with the supp in high dose
```{r, echo=TRUE, cache=TRUE}
d3<-ToothGrowth[ToothGrowth$dose==2.0,]
t.test(d3[d3$supp=="VC",]$len, d3[d3$supp=="OJ",]$len, paired=FALSE, var.equal=FALSE)
```
The 95% percent confidence interval contains 0, that means we can't reject the null hypothesis. Means in high dose, we can't say tooth len relate to supp.

# Conclusion
1. ToothGrowth is related to dose.
2. In low and medium dose, ToothGrowth len is related to supp.
3. In high dose == 2.0, there is no obvious relationship with supp.